### 2015-05-15 Manuscript/Missing_mammals-draft.tex
Abstract ideas?

\newpage
\begin{abstract}

\end{abstract}

>>>>

\newpage
\begin{abstract}
Studying changes in global biodiversity through time and space is essential.
For that we need methods to combine both palaeontological and neontological data.
One promising method, the Total Evidence method, allows such thing but needs a lot of data.
Especially morphological data from living taxa to allow the fossil taxa to accurately branch in the trees.
Despite two centuries of morphological studies on living taxa, scientists using and generating such data mainly focus on palaeontological data.
Therefore, even in well known groups such as mammal, there is a huge gap in our knowledge of morphological data for living mammals.
In this study, using phylogenetic community structure methods, we quantify the availability of data in each mammalian order.
And maybe at the end of the paper we propose some discussion on how to improve all that (go in museums!).
\end{abstract}
